This script is applied to the singlepools and does three things
1) It imports the singlepool OTU tables.  
2) Then it carries out a phyloseq analysis of OTU sizes to choose a minimum OTU size, and filters out the smaller OTUs. The missing sample in H1 is removed from the dataset.
3) Finally, it calculates NMDS ordinations and ordination plots for all singlepools. Figures 3, S_3, S_4

```{r setup chunk, message=FALSE}
# copy the following into each script   
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = FALSE
)

# script-specific libraries
library(vegan)
library(car)
library(RColorBrewer) # for colours
library(phyloseq)
library(data.table)

# general-use packages
library(here)
library(tidyverse) 
library(readxl)
library(cowplot)
library(lubridate)
library(patchwork)
library(arsenal) # for summary(comparedf())
library(sjmisc) # for rotate_df()
library(envDocument)
library(conflicted)
  conflict_prefer("mutate", "dplyr", quiet = TRUE)
  conflict_prefer("select", "dplyr", quiet = TRUE)
  conflict_prefer("summarise", "dplyr", quiet = TRUE)
  conflict_prefer("filter", "dplyr", quiet = TRUE)
  conflict_prefer("first", "dplyr", quiet = TRUE)
  conflict_prefer("here", "here", quiet = TRUE)
  conflict_prefer("separate", "tidyr", quiet = TRUE)
  conflict_prefer("unite", "tidyr", quiet = TRUE)
  conflict_prefer("intersect", "dplyr", quiet = TRUE)
  conflict_prefer("year", "lubridate", quiet = TRUE)
  conflict_prefer("setdiff", "dplyr", quiet = TRUE) 
  
# Provide real numbers, not scientific notation.
options(scipen = 999)
```

Import singlepool OTU tables. These tables include all OTUs, not just Arthropoda-assigned OTUs, and are not Begum filtered because filtering merges the three PCRs. This test is therefore a test based on the full dataset, including control samples
```{r import singlepool tables}
splfiles <- "table_BioSoupII_97_\\w\\d_SnglPl\\.txt"
spl_files <- list.files(Sys.glob(file.path("..", "analysis", "singlepools")), pattern = splfiles, full.names = TRUE)
    # list.files is used to look for files matching "table_BioSoupII_97_\\w\\d_SnglPl\\.txt"
    # full.names = TRUE returns the pathnames
    # \\ is used to escape \ and . (because otherwise they are read with grep as "ignore" and "any character". R needs a second \)
head(spl_files); cat("    ", length(spl_files), "total files")

# column names of spl files
spl_cols <- c("OTU_ID","Hhmlbody","Hhmlleg","hhhlbody","hhhlleg","hlllbody","hlllleg","mmmmbody","mmmmleg")

# function to read_tsv the files
readsnglpools <- function(x) {
    df <- read_tsv(x, na = "NA") 
    df
}
spl <- map(spl_files, readsnglpools)

# name dfs in spl list
folderpoolvec <- sub("table_BioSoupII_97_(\\w\\d)_SnglPl\\.txt", "\\1", basename(spl_files), perl=TRUE)
names(spl) <- folderpoolvec

# individual singlepools can be referred to as spl$folderpool: spl$A1
```

phyloseq filtering by OTU size. This step removes "small" OTUs, which are probably artefacts of PCR and sequencing error, i.e. echo OTUs, which should have been clustered into the legitimate OTUs. What is "small"?  It is a bit subjective, but the phyloseq method helps us make a judgement. Phyloseq creates a rarefaction curve, showing how many OTUs would be removed at each minimum OTU size. A minimum OTU size is set at the tangent to this curve. See the graphs created below to understand this.

The reason for using phyloseq OTU-size filtering is because the singlepool analysis cannot use Begum filtering to remove false-positive sequences. 

Strategy:  survey a sample of OTU tables to decide on a common min OTU size. Then apply a function to all OTU tables in the spl list.
```{r phyloseq analysis, eval=FALSE}
# choose a table
communityAll_t <- spl$A1 # starting with PCRA1

# Inspect the control sample (PC, PCR, xb) OTUs and filter the OTU table.  
communityAll_t <- communityAll_t %>% arrange(desc(PC))
# View(communityAll_t)
communityAll_t <- communityAll_t %>% select(-starts_with("PC"), -starts_with("xb"))

# Transpose to make canonical OTU tables (sample X OTU format) for community analysis
communityAll <- rotate_df(communityAll_t, cn = TRUE)
# OTU sizes are the colSums (not the number of reads within each cell)
# colSums(communityAll)

# phyloseq code
TotalCounts <- c(colSums(communityAll))
tdt = data.table(OTUs = colnames(communityAll), TotalCounts = colSums(communityAll), OTU = colnames(communityAll))
taxcumsum = tdt[, .N, by = TotalCounts]
setkey(taxcumsum, TotalCounts)
taxcumsum[, CumSum := cumsum(N)]
# Define the plot
(pCumSum = ggplot(taxcumsum, aes(TotalCounts, CumSum)) + 
  geom_point() + 
  xlab("Filtering Threshold:  Minimum Read Number per OTU") +
  ylab("OTUs That Would Be Filtered Out") +
  ggtitle("Number of OTUs that would be filtered out at different minimum OTU size thresholds") + 
    scale_x_continuous(breaks = scales::pretty_breaks(n = 25), limits = c(0, 100)) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 25)))
```

I look to see if the curve starts with a near-vertical rise, which indicates a large number of very small OTUs. After viewing multiple OTU tables, I have set the min OTU size threshold to be 9, which is roughly the x-intercept of the tangent to the curve in the limits=c(0,100) plot. For instance, in spl$B1, setting threshold_otu_size==9 means that 1100 OTUs are removed, which is most of them. 
```{r filter OTU tables for minimum OTU size and to set cells==1 to 0}
threshold_otu_size <- 9

minOTUsizefilter <- function(df){
    df <- df %>% select(-starts_with("PC"), -starts_with("xb")) # tidyverse
    df <- rotate_df(df, cn = TRUE) # sjmisc
    df <- df[, colSums(df) >= threshold_otu_size] # base R
    df[df == 1] <- 0 # base R
    df
}

splminOTU <- map(spl, minOTUsizefilter)

# splminOTU <- minOTUsizefilter(spl$A1)
# View(splminOTU)
# rm(splminOTU)
```

Check that all samples (rows) still have sufficient numbers of reads in them.  This isn't a risk with this dataset, but some datasets have samples with few, low-read-number OTUs. Removing small OTUs will sometimes produce samples (rows) that have almost no data, because that sample failed during PCR or DNA extraction. 
```{r}
tablerowsums <- map_dfr(splminOTU, rowSums)
View(tablerowsums)
```

In PCR H1, we find that the hhhlbody sample has no reads after filtering, which is probably because the PCR failed. Thus, the h1/hhhlbody results will overestimate dropout. 

For ordinations, we need to remove H1:hhhlbody
```{r remove hhhlbody from H1}
splminOTU[["H1"]] <- splminOTU[["H1"]] %>% 
    rownames_to_column() %>% 
    filter(rowname != "hhhlbody") %>% 
    column_to_rownames()

tablerowsums2 <- map_dfr(splminOTU, rowSums)
View(tablerowsums2)
```


Plot NMDS of every singlepool, generates 3 screens of plots:  A1-H3
```{r ordinations and plot ordinations}
(colorvec <- c("#EF8A62", "#67A9CF"))  # from:  brewer.pal(3,"RdBu")

extract_env <- function(x){
    ## extract env variables
    env <- x %>%
        rownames_to_column() %>% 
        select(sample = rowname) %>% 
        mutate(
            bodypart = case_when(
                grepl("body", sample) == TRUE ~ "body",
                grepl("leg", sample) == TRUE ~ "leg"
            )
        ) %>%
        mutate(
            bodypartcolor = if_else(bodypart == "body", 1, 2)
        ) %>% 
        mutate(
            evenness = str_remove(sample, c("body|leg"))
        )
    env$sprichness <- specnumber(x, MARGIN = 1)
    env
}
ordination <- function(x){
    df <- metaMDS(x, distance = "bray", trymax = 40, binary=FALSE)
    df
}
ordinationplot <- function(x, y, z){
  xlim <- c(-1.5, 1.0) 
  ylim <- c(-1.0, 1) 
  plot(x, ylab="", xlab="", xlim=xlim, ylim=ylim, type="n", main=y) 
   
  points(x, display = "sites", pch=16, cex=(z$sprichness/40), col=colorvec)
  
  with(z, legend("top", legend = unique(bodypart), bty = "n", col=colorvec, pt.cex=2, pch=16))
  
  cexnum <- 0.5
  
  with(z, ordispider(x, evenness, cex=cexnum, col=c("black"), label=TRUE, show.groups=(c("hlll"))))
  with(z, ordispider(x, evenness, cex=cexnum, col=c("black"), label=TRUE, show.groups=(c("Hhml"))))
  with(z, ordispider(x, evenness, cex=cexnum, col=c("black"), label=TRUE, show.groups=(c("hhhl"))))
  with(z, ordispider(x, evenness, cex=cexnum, col=c("black"), label=TRUE, show.groups=(c("mmmm"))))
}

splminOTU_all <- splminOTU

# optional: plot stressplots
stressplotfxn <- function(x){
    stressplot(x)
}
par(mfrow=c(2,3))
ordinations <- map(splminOTU_all, ordination)
map(ordinations, stressplotfxn)
par(mfrow=c(1,1))


# ordinations and ordination plots for A,B,C,D,G
splminOTU_ABCDG <- splminOTU_all[c(1:12,19:21)]
# extract env data
envs <- map(splminOTU_ABCDG, extract_env)
# run metaMDS
ordinations <- map(splminOTU_ABCDG, ordination)
# extract names of the jmds elements
plottitle <- names(ordinations)
# plot ordinations, with jmds names as plot titles
par(mfrow=c(2,3))
pmap(list(ordinations, plottitle, envs), ordinationplot)

# now plot H1
extract_env_H1 <- function(x){
    ## extract env variables
    env <- x %>%
        rownames_to_column() %>% 
        select(sample = rowname) %>% 
        mutate(
            bodypart = case_when(
                grepl("body", sample) == TRUE ~ "body",
                grepl("leg", sample) == TRUE ~ "leg"
            )
        ) %>%
        mutate(
            bodypartcolor = if_else(bodypart == "body", 1, 2)
        ) %>% 
        mutate(
            evenness = str_remove(sample, c("body|leg"))
        ) %>% 
        filter(sample != "hhhlbody")
    env$sprichness <- specnumber(x, MARGIN = 1)
    env
}

ordinationplot_H1 <- function(x, y, z){
  xlim <- c(-1.5, 1.0)
  ylim <- c(-1, 1)
  plot(x, ylab="", xlab="", xlim=xlim, ylim=ylim, type="n", main=y)
  points(x, display = "sites", pch=16, cex=(z$sprichness/40), col=colorvec)
  
  with(z, legend("top", legend = unique(bodypart), bty = "n", col=colorvec, pt.cex=2, pch=16))
  
  cexnum <- 0.5
  
  with(z, ordispider(x, evenness, cex=cexnum, col=c("black"), label=TRUE, show.groups=(c("hlll"))))
  with(z, ordispider(x, evenness, cex=cexnum, col=c("black"), label=TRUE, show.groups=(c("Hhml"))))
  with(z, ordispider(x, evenness, cex=cexnum, col=c("black"), label=TRUE, show.groups=(c("hhhl"))))
  with(z, ordispider(x, evenness, cex=cexnum, col=c("black"), label=TRUE, show.groups=(c("mmmm"))))
}

splminOTU_H1 <- splminOTU_all["H1"]
envs <- map(splminOTU_H1, extract_env_H1)
# run metaMDS
ordinations <- map(splminOTU_H1, ordination)
# extract names of the jmds elements
plottitle <- names(ordinations)
# plot ordinations, with H1 as plot title
pmap(list(ordinations, plottitle, envs), ordinationplot_H1)

# finally plot H2 and H3
splminOTU_H2H3 <- splminOTU_all[c(23,24)]
envs <- map(splminOTU_H2H3, extract_env)
# run metaMDS
ordinations <- map(splminOTU_H2H3, ordination)
# extract names of the jmds elements
plottitle <- names(ordinations)
# plot ordinations, with jmds names as plot titles
pmap(list(ordinations, plottitle, envs), ordinationplot)

par(mfrow=c(1,1))
```

```{r Welchs t-test}
t.test2 <- function(m1,m2,s1,s2,n1,n2,m0=0,equal.variance=FALSE)
{
  if( equal.variance==FALSE ) 
  {
    se <- sqrt( (s1^2/n1) + (s2^2/n2) )
    # welch-satterthwaite df
    df <- ( (s1^2/n1 + s2^2/n2)^2 )/( (s1^2/n1)^2/(n1-1) + (s2^2/n2)^2/(n2-1) )
  } else
  {
    # pooled standard deviation, scaled by the sample sizes
    se <- sqrt( (1/n1 + 1/n2) * ((n1-1)*s1^2 + (n2-1)*s2^2)/(n1+n2-2) ) 
    df <- n1+n2-2
  }      
  t <- (m1-m2-m0)/se 
  dat <- c(m1-m2, se, t, round(df,1), 2*pt(-abs(t),df))    
  names(dat) <- c("Difference of means", "Std Error", "t", "df", "p-value")
  return(dat) 
}
```


plot Procrustes plots for A vs B:  optimal Ta and optimal cycle number
```{r procrustes A B}
# calculate all ordinations
ordinations <- map(splminOTU_all, ordination)

# same tags at optimal Tm, 3 such comparisons
# A1:B1, A2:B2, A3:B3
protestA1B1 <- protest(ordinations$A1, ordinations$B1)
protestA2B2 <- protest(ordinations$A2, ordinations$B2)
protestA3B3 <- protest(ordinations$A3, ordinations$B3)


# different tags at optimal temperature, n = 12 such comparisons
# A1:A2, A1:A3, A2:A3, A1:B2, A1:B3, A2:B1, A2:B3, A3:B1, A3:B2, B1:B2, B1:B3, B2:B3
# procrustes tests
protestA2A1 <- protest(ordinations$A2, ordinations$A1)
protestA1A3 <- protest(ordinations$A1, ordinations$A3)
protestA2A3 <- protest(ordinations$A2, ordinations$A3)
protestA1B2 <- protest(ordinations$A1, ordinations$B2)
protestA1B3 <- protest(ordinations$A1, ordinations$B3)
protestA2B1 <- protest(ordinations$A2, ordinations$B1)
protestA2B3 <- protest(ordinations$A2, ordinations$B3)
protestA3B1 <- protest(ordinations$A3, ordinations$B1)
protestA3B2 <- protest(ordinations$A3, ordinations$B2)
protestB1B2 <- protest(ordinations$B1, ordinations$B2)
protestB1B3 <- protest(ordinations$B1, ordinations$B3)
protestB2B3 <- protest(ordinations$B2, ordinations$B3)

# plot the procrustes superimposition graphs.
# Top row Procrustes are between libraries using the same tags. The rest of the rows are between libraries using different tags.
par(mfrow=c(4,4))
plot(protestA1B1, main = "A1 vs B1")
plot(protestA2B2, main = "A2 vs B2")
plot(protestA3B3, main = "A3 vs B3")
plot(0,type='n',axes=FALSE,ann=FALSE, main="Top row is between same tags")
plot(protestA1A3, main = "A1 vs A3")
plot(protestA1B2, main = "A1 vs B2")
plot(protestA1B3, main = "A1 vs B3")
plot(protestA3B1, main = "A3 vs B1")
plot(protestA3B2, main = "A3 vs B2")
plot(protestB1B2, main = "B1 vs B2")
plot(protestB1B3, main = "B1 vs B3")
plot(protestB2B3, main = "B2 vs B3")
plot(protestA2A1, main = "A2 vs A1")
plot(protestA2A3, main = "A2 vs A3")
plot(protestA2B1, main = "A2 vs B1")
plot(protestA2B3, main = "A2 vs B3")
par(mfrow=c(1,1))

# store correlation coefficients from Protest
# pairwiseAB <- c("A2A1", "A1A3", "A2A3", "A1B2", "A1B3", "A2B1", "A2B3", "A3B1", "A3B2", "B1B2", "B1B3", "B2B3")
pairwiseAB_sametags <- c("A1B1", "A2B2", "A3B3")
pairwiseAB_difftags <- c("A1A3","A1B2","A1B3","A3B1","A3B2","B1B2","B1B3","B2B3","A2A1","A2A3","A2B1","A2B3")
correlationsAB_sametags <- 0
j=0
for (i in pairwiseAB_sametags) {
  j=j+1
  correlationsAB_sametags[j] <- get(paste0("protest", i))[["scale"]] # correlation coefficient from protest 
}

correlationsAB_difftags <- 0
j=0
for (i in pairwiseAB_difftags) {
  j=j+1
  correlationsAB_difftags[j] <- get(paste0("protest", i))[["scale"]] # correlation coefficient from protest 
}

correlationsAB_sametags
(n1 <- length(correlationsAB_sametags))
(m1 <- mean(correlationsAB_sametags))
(s1 <- sd(correlationsAB_sametags))
# (s1 <- sd(correlationsAB_sametags)/sqrt(length(correlationsAB_sametags)))

correlationsAB_difftags
(n2 <- length(correlationsAB_difftags))
(m2 <- mean(correlationsAB_difftags))
(s2 <- sd(correlationsAB_difftags))
# (s2 <- sd(correlationsAB_difftags)/sqrt(length(correlationsAB_difftags)))

(ABsinglepoolstest <- t.test2(m1, m2, s1, s2, n1, n2))
```

plot Procrustes plots for C vs D
high Ta and optimal cycle number
```{r procrustes C D}
protestC1D1 <- protest(ordinations$C1, ordinations$D1)
protestC2D2 <- protest(ordinations$C2, ordinations$D2)
protestC3D3 <- protest(ordinations$C3, ordinations$D3)

# different tags at higher than optimal temperature, n = 12 such comparisons
# C1:C2, C1:C3, C2:C3, C1:D2, C1:D3, C2:D1, C2:D3, C3:D1, C3:D2, D1:D2, D1:D3, D2:D3
# procrustes tests
  protestC1C2 <- protest(ordinations$C1, ordinations$C2)
  protestC1C3 <- protest(ordinations$C1, ordinations$C3)
  protestC2C3 <- protest(ordinations$C2, ordinations$C3)
  protestC1D2 <- protest(ordinations$C1, ordinations$D2)
  protestC1D3 <- protest(ordinations$C1, ordinations$D3)
  protestC2D1 <- protest(ordinations$C2, ordinations$D1)
  protestC2D3 <- protest(ordinations$C2, ordinations$D3)
  protestC3D1 <- protest(ordinations$C3, ordinations$D1)
  protestC3D2 <- protest(ordinations$C3, ordinations$D2)
  protestD1D2 <- protest(ordinations$D1, ordinations$D2)
  protestD1D3 <- protest(ordinations$D1, ordinations$D3)
  protestD2D3 <- protest(ordinations$D2, ordinations$D3)

# plot the procrustes superimposition graphs.
# Top row Procrustes are between libraries using the same tags. The rest of the rows are between libraries using different tags.
par(mfrow=c(4,4))
plot(protestC1D1, main = "C1 vs D1")
plot(protestC2D2, main = "C2 vs D2")
plot(protestC3D3, main = "C3 vs D3")
plot(0,type='n',axes=FALSE,ann=FALSE, main="Top row is between same tags")
plot(protestC1C2, main = "C1 vs C2")
plot(protestC1C3, main = "C1 vs C3")
plot(protestC2C3, main = "C2 vs C3")
plot(protestC1D2, main = "C1 vs D2")
plot(protestC1D3, main = "C1 vs D3")
plot(protestC2D1, main = "C2 vs D1")
plot(protestC2D3, main = "C2 vs D3")
plot(protestC3D1, main = "C3 vs D1")
plot(protestC3D2, main = "C3 vs D2")
plot(protestD1D2, main = "D1 vs D2")
plot(protestD1D3, main = "D1 vs D3")
plot(protestD2D3, main = "D2 vs D3")
par(mfrow=c(1,1))


# store correlation coefficients from Protest
pairwiseCD_sametags <- c("C1D1","C2D2","C3D3")
pairwiseCD_difftags <- c("C1C2", "C1C3", "C2C3", "C1D2", "C1D3", "C2D1", "C2D3", "C3D1", "C3D2", "D1D2", "D1D3", "D2D3")
correlationsCD_sametags <- 0
j=0
for (i in pairwiseCD_sametags) {
  j=j+1
  correlationsCD_sametags[j] <- get(paste0("protest", i))[["scale"]] # correlation coefficient from protest 
}

correlationsCD_difftags <- 0
j=0
for (i in pairwiseCD_difftags) {
  j=j+1
  correlationsCD_difftags[j] <- get(paste0("protest", i))[["scale"]] # correlation coefficient from protest 
}

correlationsCD_sametags
(n1 <- length(correlationsCD_sametags))
(m1 <- mean(correlationsCD_sametags))
(s1 <- sd(correlationsCD_sametags))

correlationsCD_difftags
(n1 <- length(correlationsCD_difftags))
(m2 <- mean(correlationsCD_difftags))
(s2 <- sd(correlationsCD_difftags))

(CDsinglepoolstest <- t.test2(m1, m2, s1, s2, n1, n2))
```

plot Procrustes plots for G and H (omitting H1)
Touchdown PCR
```{r procrustes G H}
# H1 cannot be used because it is is missing one sample: hhhlleg

# protestG1H1 <- protest(ordinations$G1, ordinations$H1) 
protestG2H2 <- protest(ordinations$G2, ordinations$H2)
protestG3H3 <- protest(ordinations$G3, ordinations$H3)


# different tags at higher than optimal temperature, n = 8 such comparisons
# G1:G2, G1:G3, G2:G3, G1:H2, G1:H3, G2:H3, G3:H2, H2:H3
# procrustes tests
  protestG1G2 <- protest(ordinations$G1, ordinations$G2)
  protestG1G3 <- protest(ordinations$G1, ordinations$G3)
  protestG2G3 <- protest(ordinations$G2, ordinations$G3)
  protestG1H2 <- protest(ordinations$G1, ordinations$H2)
  protestG1H3 <- protest(ordinations$G1, ordinations$H3)
  # protestG2H1 <- protest(ordinations$G2, ordinations$H1)
  protestG2H3 <- protest(ordinations$G2, ordinations$H3)
  # protestG3H1 <- protest(ordinations$G3, ordinations$H1)
  protestG3H2 <- protest(ordinations$G3, ordinations$H2)
  # protestH1H2 <- protest(ordinations$H1, ordinations$H2)
  # protestH1H3 <- protest(ordinations$H1, ordinations$H3)
  protestH2H3 <- protest(ordinations$H2, ordinations$H3)

# plot the procrustes superimposition graphs.
# Top row Procrustes are between libraries using the same tags. The rest of the rows are between libraries using different tags.
par(mfrow=c(3,4))
# plot(protestG1H1, main = "G1 vs H1")
plot(protestG2H2, main = "G2 vs H2")
plot(protestG3H3, main = "G3 vs H3")
plot(0,type='n',axes=FALSE,ann=FALSE, main="Top row is between same tags")
plot(0,type='n',axes=FALSE,ann=FALSE, main="Top row is between same tags")
plot(protestG1G2, main = "G1 vs G2")
plot(protestG1G3, main = "G1 vs G3")
plot(protestG2G3, main = "G2 vs G3")
plot(protestG1H2, main = "G1 vs H2")
plot(protestG1H3, main = "G1 vs H3")
# plot(protestG2H1, main = "G2 vs H1")
plot(protestG2H3, main = "G2 vs H3")
# plot(protestG3H1, main = "G3 vs H1")
plot(protestG3H2, main = "G3 vs H2")
# plot(protestH1H2, main = "H1 vs H2")
# plot(protestH1H3, main = "H1 vs H3")
plot(protestH2H3, main = "H2 vs H3")
par(mfrow=c(1,1))


# store correlation coefficients from Protest
pairwiseGH_sametags <- c("G2H2","G3H3")
pairwiseGH_difftags <- c("G1G2", "G1G3", "G2G3", "G1H2", "G1H3", "G2H3", "G3H2", "H2H3")
correlationsGH_sametags <- 0
j=0
for (i in pairwiseGH_sametags) {
  j=j+1
  correlationsGH_sametags[j] <- get(paste0("protest", i))[["scale"]] # correlation coefficient from protest 
}

correlationsGH_difftags <- 0
j=0
for (i in pairwiseGH_difftags) {
  j=j+1
  correlationsGH_difftags[j] <- get(paste0("protest", i))[["scale"]] # correlation coefficient from protest 
}

correlationsGH_sametags
(n1 <- length(correlationsGH_sametags))
(m1 <- mean(correlationsGH_sametags))
(s1 <- sd(correlationsGH_sametags))

correlationsGH_difftags
(n2 <- length(correlationsGH_difftags))
(m2 <- mean(correlationsGH_difftags))
(s2 <- sd(correlationsGH_difftags))

(GHsinglepoolstest <- t.test2(m1, m2, s1, s2, n1, n2))
```



<details>
<summary>Reproducibility receipt</summary>
```{r}
# datetime
Sys.time()

# repository
git2r::repository(here::here())

envDocument::env_doc("table", git = FALSE)
```
